I would like to express my gratitude and appreciation to my Ph.D. advisor, Prof. Alexandru Ionescu, for his support, guidance, and mentorship throughout the journey of my Ph.D. program. I feel extremely fortunate to have had the opportunity to work under his supervision.

I am also grateful to the professors with whom I have had the privilege of interacting during the journey of my Ph.D. program, for their invaluable guidance, constructive feedback, and encouragement. My thanks go to Professors Tristan Buckmaster, Yu Deng, Zaher Hani, Hao Jia, Igor Rodnianski, Jalal Shatah, Ze Li and Lifeng Zhao for their enlightening discussions and generous assistance.

My heartfelt thanks go to my fellow math Ph.D. students, who have made this journey all the more enjoyable and memorable. I am particularly thankful for the friendship and support of Shaoyun Bai, Jiajie Chen, Shengwen Gan, Vikram Giri, Lili He, Kexin Jin, Yangyang Li, Federico Pasqualotto, Shuangping Li, Jia Shi, Zhihan Wang, Xiaoxu Wu, Lingfu Zhang, Junyan Zhang, Fan Zheng, and many others I encountered who have been there for me during the highs and lows of this journey. I would like to express my special gratitude to Zhihan Wang, Kexin Jin, and Fan Zheng. During the five years Ph.D. program, Zhihan Wang and Kexin Jin shared uncountable many invaluable and genius ideas from which I have learned a great deal.  Fan Zheng, as my senior, has taught me much during my first year, and his mentorship has been instrumental in my growth as a researcher.


During my time in the Ph.D. program, I have been fortunate to be surrounded by an amazing group of friends who have not only inspired me but also enriched my graduate school experience. I would like to express my gratitude to Yixiao Chen, Yifan Chen, Zihan Ding, Hansheng Jiang, Shiji Lyu, Zhou Lu, Xiaohan Li, Qinghua Liu, Pinchen Xie, Shouda Wang, Baojun Wu, Qinxin Yan, Yucheng Yang, Bingjia Yang, Zhiyang Yuan, Xiyu Zhai and many others I encountered. I would like to extend a special thanks to Yifan Chen, for her support during the Covid pandemic. Additionally, I also want to express my special appreciation to Yixiao Chen, Zihan Ding, Qinghua Liu, Shouda Wang, and Yucheng Yang for frequently giving me rides and spending leisure time.

Finally, I dedicate this thesis to my loving family, who has been my constant source of motivation and support. As always, I owe much more to my family than I can ever hope to give back. Thank you, mom, dad, for your unconditional love and support!

\newpage

\ 

\vspace{20em}

\rightline{\textit{To my family and friends. }}